New insights into the Weddell Sea ecosystem applying a network approach

### 2022-08-19 Manuscript/Manuscript.Rmd
Estimation phytodetritus & sediment strength

We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012]. The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality. On one hand, resource density scales with resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources 'detritus' and 'sediment' were not available in GATEWAy, we estimated it considering the scaling relationship with consumer mass, also different in 2D and 3D (for details see equation S9 and figures 2c-d of Supplementary Information in @Pawar2012). On the other hand, search rate scales with consumer mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.

>>>>

We obtained estimations for the resource density and the search rate from the scaling relationships with the resource and the consumer mass, respectively [@Pawar2012]. The coefficients of such relationships, determined by ordinary least squares regression, vary with the interaction dimensionality. On one hand, resource density scales with resource mass as a power-law with exponents \vec{p = -0.79 \pm 0.09} in 2D and \vec{p = -0.86 \pm 0.06} in 3D. Since mean mass for resources 'phytodetritus' and 'sediment' were not available in GATEWAy, we considered the body mass of the smallest phytoplankton species ('Fragilariopsis cylindrus') as a proxy. This is justified by the fact that 'phytodetritus' and 'sediment' are mainly composed by dead or senescent phytoplankton reaching the seabed (@Wolanski2011). On the other hand, search rate scales with consumer mass as a power-law with exponents \vec{p = 0.68 \pm 0.12} in 2D and \vec{p = 1.05 \pm 0.08} in 3D.
